### 2016-03-22 section/5_exper.tex
rough pass of results

First, we evaluate \Tool on 18 out of the 45 bugs listed in Table \ref{tab:root}. 
Among these 18, seven are extracted from Java or JavaScript
programs and re-implemented in C++, as \Tool currently only handles C/C++
programs; one is extracted from a very old version of Mozilla.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
%The extraction is conducted by XXX.
We extract the original data structures and caller-callees, 
and translate them into C++ programs, following the original data flow and control flow dependence. 
We design unit test inputs based on inputs in bug reports and our understanding to run our re-implemented codes.  
We did not use the remaining 27 bugs listed in Table \ref{tab:root}
as benchmarks, 
either because they depend on special hardware/software environment
or because they involve too complex data structures to extract. 
For example, some bugs can only be triggered on Windows, and some bugs depend on .Net libraries. 
For example, we have bugs related to GUI widgets, and it is too complex to re-implement these GUI widgets. 
We also have bugs, in which buggy loops traverse graphs. 
Without repeating these bugs, it is too difficult to figure out graph structures just through code reading.  
Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
shown in Table~\ref{tab:benchmarks}.

Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama}.
We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
All these bugs are related to misusing basic data structures in Java, like ArrayList, HashSet, HashMap, and LinkedList. 
We re-implement these basic data structures following the recent version of openjdk. 
We re-implement the buggy codes and test inputs in the bug reports, 
following the original data flow and control flow dependence. 
For two benchmarks, there are only 4 loops in our re-implemented versions. For all other benchmarks, there are no less than 5 loops. 
Note that, Toddler focuses on inefficient nested loops, and its
benchmark bugs only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.
We use Toddler benchmark suite because it provides a large set of
repeatable inefficient loop problems.

@@

\paragraph{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For 14 out of the 18 benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining
benchmarks, the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.
%XXX (what can we say about Toddler benchmark set here?)
For all benchmarks from Toddler project, 
statistical debugging ranks the real root-cause loop as Top 1 or Top 2 (for cases where there are two root-cause loops). 
During our accuracy experiments, we will apply LDoctor to top 5 loops identified by statistical debugging. 
For some re-implemented bugs, there may be less than 5 loops returned by statistical debugging. 
The number of loops we analyze for the first benchmark set is 64, and the number of loops we analyze for Toddler benchmark set is 103.

@@

The six cases where the fix strategy suggested by \Tool does not match that of 
developers fall into three categories.
First, the fix strategy taken by developers is a subset of what suggested by 
\Tool.
For MySQL\#27287, the root-cause loop
is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
only changed the data structure, which eliminated both types of inefficiency,
in case of MySQL\#27287. 
For Apache\#53622, there are two buggy loops, one is cross-loop redundant, and the other is 0*1? Inefficient. 
\Tool suggests batching and changing data structure respectively. 
In practice, developers only fix the main root cause loop, by using changing data structure.

Second, the fix strategy taken by developers is a superset of what suggested by
\Tool.
In Collections bugs \#407, \#408, and \#425, XXX.

@@

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 11 out of the
13 benign cases (XXX subject to change XXX). 
In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging can accurately
tell that these loops are not top contributors to the performance
problems.
Two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.
The remaining cases XXX.

The accuracy of \Tool benefits from its run-time analysis.
For example, there are 7 (XXX to change XXX) benchmarks in total that each contains
a loop that generates side effect only
in its last iteration. Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the total number of iterations and
correctly identifies 3 (XXX to change XXX) of them as truly inefficient and severe enough
to cause the corresponding performance problem.

@@

\subsection{Comparison with other tools}
XXXXXX

>>>>

First, we evaluate \Tool on all bugs, 18 in total, that we can reproduce 
among the 45 bugs listed in Table \ref{tab:root}. 
Among these 18, seven are extracted from Java or JavaScript
programs and re-implemented in C++, as \Tool currently only handles C/C++
programs; one is extracted from a very old version of Mozilla that can no longer be
compiled as it is.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
%The extraction is conducted by XXX.
When we extract code, we try our best to keep all bug-related data structures,
caller functions, and callee functions intact, and re-implement them in C++, 
following the original data flow and control flow. For these extracted benchmarks, 
we design bug-triggering inputs for them based on the bug-triggering inputs in 
the original bug reports and our understanding about how original program inputs
map to the inputs of our re-implemented programs.
Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
shown in Table~\ref{tab:benchmarks}. 
We will refer to this set of bugs as our \emph{general} benchmark suite.

Note that, we expect \Tool algorithm to also work for the remaining 27 bugs 
listed in Table \ref{tab:root}, but they are too difficult to be reproduced
on our machines.
First, they all depend on 
special hardware/software environment that our machine is not equipped with.
For example, some bugs can only be triggered on Windows, and some bugs depend on 
.Net libraries. 
Furthermore, the bug-related code for these 27 cases
cannot be easily extracted or reimplemented, as we did for the eight 
benchmarks mentioned above. 
For example, some bugs are related to GUI widgets, which are too complicated to 
re-implement or emulate. As another example, some bugs' inefficient 
loops traverse big graphs. Although we can extract the buggy code regions, it is 
too difficult to figure out the bug-triggering inputs
(i.e., the graphs) without reproducing the original bugs.

%Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
%{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
%All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
Second, we evaluate \Tool on Toddler~\cite{Alabama, toddlerbuglist} benchmark suite.
Toddler project provides the bug-triggering inputs and detailed explanation
for 21 inefficient-loop bugs that have been confirmed and fixed by developers, and
we evaluate \Tool on \emph{all} of these 21 bugs.
Due to the focus of Toddler, all of these bugs 
are related to misusing basic data structures in Java, like ArrayList, HashSet, 
HashMap, and LinkedList. We extract these bugs and re-implemented them in 
C/C++, following the procedure discussed above. In doing so,
we also re-implement basic Java data structures following a recent version of 
\texttt{openjdk}. At the end, each extracted benchmark contains at least five
loops, except for two cases where only 4 loops exist in the extracted version. 
Note that, Toddler focuses on inefficient nested loops, and hence its
benchmark bugs only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.

We use Toddler benchmark suite for two reasons.
First, it was set up for completely different reasons and methodology from our
\emph{general} benchmark suite,
and hence can well complement the latter suite.
Second, it provides the largest set of 
repeatable inefficient loop problems that we can find.

@@

\paragraph{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For all but four benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining four
benchmarks, which all come from Table \ref{tab:root},
the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.
%XXX (what can we say about Toddler benchmark set here?)

@@

The six cases where the fix strategy suggested by \Tool does not match that of 
developers fall into three categories.
First, the fix strategy taken by developers is a subset of what suggested by 
\Tool.
For MySQL\#27287 and Apache\#53622, the root-cause loops contain both
cross-loop redundancy and 0*1? inefficiency. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
acknowledge both types of inefficiencies, but the patches
only changed the data structures, which eliminated both types of inefficiencies 
in case of MySQL\#27287 and left the cross-loop redundancy unsolved in
Apache\#53622. 
%For Apache\#53622, there are two buggy loops, one is cross-loop redundant, and the other is 0*1? inefficient. 
%\Tool suggests batching and changing data structure, respectively. 
%In practice, developers only fix the main root cause loop, by using changing data structure.}

Second, the fix strategy taken by developers is related but not exactly the same as
what suggested by \Tool.
The root-cause loops in 
Collections bugs \#407, \#408, and \#425 all conduct frequent linear searches in arrays.
\Tool suggests data-structure changes for these three cases. Developers' patches 
still keep the original data structure and the original buggy loop, but they
did use hash-sets, which contain the same content as the arrays do,
to help conditionally skip the loops.

@@

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 20 out of the
22 benign cases. % 11 out of 13 in the first benchmark set 
In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging can accurately
tell that these loops are not top contributors to the performance
problems.
Two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.

The accuracy of \Tool benefits from its run-time analysis.
%{\color{red} For example, there are 26 
For example, our run-time analysis has correctly pruned out 24 false positives
in 0*1? inefficiency detection for our benchmarks. Each of these 24 loops is a
top-5 suspicious loops in one of our benchmarks; it only generates side effect
in its last iteration, and hence is identified as by \Tool static analysis. 
Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the total number of iterations and
correctly identifies them as false positives. Similarly, \Tool run-time analysis
helps prune out 19 false positives for [0$|$1]* loop identification.

@@

\subsection{Comparison with other tools}

Automated tools have been developed to detect inefficient loop bugs
\cite{Alabama, CARAMEL, IsilDillig.PLDI15}. 
As discussed in Section \ref{sec:intro}, although these tools are very
useful, they are not suitable for failure diagnosis. 
For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
hence can only cover about half of the bugs in our \emph{general} benchmark suite.
Being a dynamic tool, it also incurs 10X or more slowdowns, which is much more
expensive than \Tool. 
Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
by adding conditional-breaks. Very few bugs in Table \ref{tab:} are like this.
CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs. 
We expect it to automatically detect a sub-set of the cross-loop redundancy
loops in our benchmark set, but not for other types of inefficient
loops. In summary, \Tool aims to explain performance problems that have 
already manifested,
yet bug detection tools aim to predict problems that may not have manifested.
\Tool achieves higher generality and accuracy at the cost of the prediction
capability.

Comparing with existing profiling and performance
statistical debugging technique \cite{SongOOPSLA2014}, \Tool provides much
more detailed root-cause information. Instead of just identifying loops that
are highly correlated-with/responsible-for the execution slowness, \Tool
can accurately point out whether these suspicious loops are efficient or not,
and which type of inefficiency a loop contains, if any, and make fix suggestions.
